Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-06-09 Journal1/paper5TNSM/pr.tex
add paper

\subsection{Motivations}

\subsection{Main Contributions}
The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.

>>>>

\subsection{Motivations}
\textcolor{MidnightBlue}{The studies in \cite{yue2021beamforming, moosavi2021delay, ali2019energy} have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively. However, this architecture is inefficient whenever we have different services with different QoS simultaneously. Additionally, RAN slicing requires a more flexible and open architecture. Therefore, we need a new architecture that supports slicing to implement RAN slicing for various services. O-RAN architecture has emerged as
a new architecture that can serve different services simultaneously using RAN slicing. In \cite{setayesh2020joint}, the RAN slicing is considered for C-RAN architecture for eMBB and URLLC. Nevertheless, the authors did not consider latency for URLLC, which is the main property of the URLLC. 
Moreover, the authors did not consider the weakness of C-RAN architecture.
In \cite{kazemifard2021minimum}, the authors examine the total delay of the UE in the O-RAN architecture. However, the paper did not consider the different services and other QoS. 
}

\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously. 
Therefore, we want to study the problem of obtaining the optimal number of VNF, RB assignments, and power allocation to maximize the system's throughput and guarantee the QoS of services. This problem is mixed-integer non-linear programming. Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.}
\subsection{Main Contributions}
The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
